Removing nonlinear batch effects using adversarial deep neural networks

### 2019-04-11 thesis.tex
Change abstract to present tense

\begin{abstract}
	The abstract text goes here.
\end{abstract}

>>>>

\begin{abstract}
	Many biological studies, particularly studies involving the genetics of human disease, could discover items of greater statistical and biological significance if performed with larger data sets.
	Many data sets are publicly available and could be combined in order to increase these studies' significance, but even when the same type of data are collected by multiple studies, minor differences in collection methodologies and environments can lead to confounding effects in the data which can in turn cause incorrect results.
	In order to do so, we applied deep learning to remove these effects and combine molecular biological data sets.
	We created an adversarial variational autoencoder in order to remove confounding effects from the data while minimizing the amount of change to the input data.
	We tested the model on artificially constructed data and commonly used real biological data sets and compared the output with the output from other common batch adjustment algorithms.
	We also applied the model to remove the tissue signal from pan-cancer data.
	Our software is available on GitHub to enable other scientists to remove confounding effects from their own data using our methodologies.
\end{abstract}
